

```{r catch.summary, include=FALSE}
library(tidyverse)

#  read in FFS data dbf      
RV.SET <- read.dbf("Data/RV_SET.dbf")
RV.Catch <- read.dbf("Data/RV_CATCH.dbf")

# match spp names to codes 
RV.Catch <- left_join(RV.Catch, spp_codes, by=c("SPECIES" = "code"))

#number of sets
sets <- length(RV.SET)

#divisions surveyed
divs <- unique(RV.SET$NAFO_DIV)

#Depth range
depth.range <- range(as.numeric(as.character(RV.SET$MEAN_DEPTH)),na.rm=TRUE)

#Number of species encountered.
num.species <- length((unique(RV.Catch$SPECIES)))

#Total catch
total.catch <- RV.Catch %>% 
  summarise(total=sum(WEIGHTC))
```

This trip completed `r sets` sets in NAFO divisions `r as.character(divs)`. Total catch was `r round (total.catch,0)`kg, with `r num.species` taxa recorded. Fishing occurred from `r min(depth.range)`m to `r max(depth.range)`m.
\

```{r top.catch, echo=FALSE}
library(tidyverse)

weight.sum <- RV.Catch %>% 
  group_by(Spc_Name) %>% 
  summarize(weight=sum(WEIGHTC)) %>% 
  arrange(desc(weight))

weight.sum$prop <- weight.sum$weight/total.catch$total

```
`r num.species` taxa were represented in the catch, with a total catch weight of `r total.catch`kg. `r as.character(weight.sum$Spc_Name[1])` and `r as.character(weight.sum$Spc_Name[2])` were the most prevalent species, accounting for `r round(weight.sum$prop[1]*100,1)`% and `r round(weight.sum$prop[1]*100,2)`% of the total catch by weight, respectively. Figure \@ref{catch.summary} summarizes the most commonly caught taxa from this trip.

Summarized near bottom temperature from a net mounted CTD is shown in Figure \@ref{temp.plot}.

```{r catch.plot, echo=FALSE, message=FALSE,fig.height = 5, fig.width = 7, fig.caption = "Total catch weight of the fifteen most commonly encountered taxa during trip `r trip"}

library(tidyverse)

RV.Catch %>% 
  group_by(SPECIES) %>% 
  summarize(weight=sum(WEIGHTC)) %>% 
  top_n(15) %>% 
  ggplot +
  geom_col(aes(x=reorder(SPECIES), -weight), y=weight)+
  scale_y_continuous(expand=c(0,0), limits=c(0,1500))+
  ylab("Total catch weight (kg)")+
  xlab("Species code")+
  theme_bw()+
  theme(axis.text=element_text(size=10),
        axis.title=element_text(size=12),
        plot.title = element_text(hjust = 0.5,size=14),
        axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0)),
        axis.title.x = element_text(margin = margin(t = 10, r = 20, b = 0, l = 0)),
        plot.margin=unit(c(0.25,1,0.5,0.25),"cm"),
        panel.border = element_rect(colour = "grey", fill=NA, size=0.75))
```


```{r temp.plot, echo=FALSE, message=FALSE, fig.height = 6, fig.width = 5, fig.caption = "Temperature at depth, as recorded from trawl mounted CTD"}
library(tidyverse)

RV.SET %>% 
  filter(FISH_TEMP<88) %>% 
  ggplot()+
  geom_point(aes(y=as.numeric(as.character(MEAN_DEPTH)), x=FISH_TEMP), size=2)+
  scale_y_reverse()+
  ylab("Depth (m)")+
  xlab("Temperature (°C)")+
  theme(axis.text=element_text(size=10),
        axis.title=element_text(size=12),
        plot.title = element_text(hjust = 0.5,size=14),
        axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0)),
        axis.title.x = element_text(margin = margin(t = 10, r = 20, b = 0, l = 0)),
        plot.margin=unit(c(0.25,1,0.5,0.25),"cm"),
        panel.border = element_rect(colour = "black", fill=NA, size=0.75))

```



This report has been prepared by `r trip_sum[["PIC"]]`(SIC).

